Model-based variable selection for regression with highly correlated variables.

### 2014-04-24 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@549 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We want to find the most probable structure $S$ knowing the dataset, so we search for the structure that maximizes $P(S|\boldsymbol{X})$ and we have:	
	\begin{eqnarray}
	 \label{approxBIC} P(S|\boldsymbol{X})&\propto & P(\boldsymbol{X}|S)P(S)
	=P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)P(\boldsymbol{X}_f|S)P(S)
	\end{eqnarray}
So we will try to maximize $\psi(\boldsymbol{X},S)=P(\boldsymbol{X}|S)P(S)$.
	The discrete structure $S$ is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(\boldsymbol{X},\boldsymbol{Y})$, the residuals ($\boldsymbol{\varepsilon}_j$) would not stay Gaussian (see the appendices).

@@

\section{Acknowledgements}
	We want to thanks ArcelorMittal Atlantique \& Lorraine that has granted this work, given the chance to use \textsc{CorReg} on real dataset and authorized the package to be open-sourced licensed (\textsc{CeCILL}), especially Dunkerque's site where most of the work has been done.
\bibliography{biblio}{}
\bibliographystyle{plain}
\section{Appendices}
	\subsection{Identifiability of the structure}
	The model presented above relies on a discrete structure $S$ between the covariates. But to find it we need identifiability property to insure the MCMC will asymptotically find the true model. Identifiability of the discrete structure is asked in following terms: Is it possible to find another structure $\tilde{S}$ of linear regression between the covariates leading to the same joint distribution and marginal distributions? The answer is no. Thus $S$ is identifiable.

	If there are exact regressions ($\sigma^2_j=0$) in (\ref{SR}), the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not really a problem. Moreover, when an exact sub-regression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. %\textsc{CorReg} (Our R package) prints a warning to point out exact regressions when found.
	In the followings we suppose $\sigma^2_j\neq 0$.

>>>>

We want to find the most probable structure $S$ knowing the dataset, so we search for the structure that maximizes $P(S|\boldsymbol{X})$ and we have:	
	\begin{eqnarray}
	 \label{approxBIC} P(S|\boldsymbol{X})&\propto & P(\boldsymbol{X}|S)P(S)
	=P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)P(\boldsymbol{X}_f|S)P(S)
	\end{eqnarray}
So we will try to maximize $\psi(\boldsymbol{X},S)=P(\boldsymbol{X}|S)P(S)$.
	The discrete structure $S$ is identifiable under some hypothesis detailed in appendix, that is we can't permute some sub-regressions in (\ref{SR}) and obtain the same joint distribution $P(\boldsymbol{X},\boldsymbol{Y})$.

@@

\section{Acknowledgements}
	We want to thanks ArcelorMittal Atlantique \& Lorraine that has granted this work, given the chance to use \textsc{CorReg} on real dataset and authorized the package to be open-sourced licensed (\textsc{CeCILL}), especially Dunkerque's site where most of the work has been done.
\bibliography{biblio}{}
\bibliographystyle{plain}
\section{Appendices}
	\subsection{Identifiability of the structure}
	The model presented above relies on a discrete structure $S$ between the covariates. But to find it we need identifiability property to insure the MCMC will asymptotically find the true model. Identifiability of the discrete structure is asked in following terms: Is it possible to find another structure $\tilde{S}$ of linear regression between the covariates leading to the same joint distribution and marginal distributions?

		If there are exact sub-regressions ($\sigma^2_j=0$), the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not really a problem. Moreover, when an exact sub-regression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. %\textsc{CorReg} (Our R package) prints a warning to point out exact regressions when found.
	In the followings we suppose $\sigma^2_j\neq 0$.

	We introduce the matricial notation
		$\boldsymbol{X}_r=\boldsymbol{X}_f\boldsymbol{\alpha} + \boldsymbol{\varepsilon}$
		we note $\Theta$ the parameter of the model. $\boldsymbol{\alpha}$ is the $(p-p_r)\times p_r$ matrix whose columns are the $\boldsymbol{\alpha}_j$.
		\\ We want to know if $P(\boldsymbol{X}|S,\Theta)=P(\boldsymbol{X}|\tilde{S},\tilde{\Theta})$ does imply $(S,\Theta)=(\tilde{S},\tilde{\Theta})$.

	\subsubsection{Identifiability of $\Theta$}		
		We know by identifiability of the Gaussian mixtures and linear regression ($\boldsymbol{X}_f'\boldsymbol{X}_f$ is of full rank) that if $P(\boldsymbol{X}|S,\Theta)=P(\boldsymbol{X}|S,\tilde{\Theta})$ then $\Theta=\tilde{\Theta}$. But the identifiability of the discrete parameter $S$ is still pending.

	\subsubsection{Sufficient conditions for Identifiability of $S$}

	In the following, $\otimes$ and $\oplus$ denote respectively the kronecker product and sum.
	\begin{eqnarray}
			\forall j \in I_r : \  \boldsymbol{X}^j_{|\boldsymbol{X}_f}&\sim & \mathcal{N}(\boldsymbol{X}_f\boldsymbol{\alpha}_j,\sigma^2_j\boldsymbol{I}_n) \label{densitycondgauche}\\
			\forall j \in I_f : \boldsymbol{X}^j_{|S} &\sim& \mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } k_j  \label{densitydroite}\\
			\textrm{And we obtain, } \forall j \in I_r : \  \boldsymbol{X}^j&\sim & 
						\mathcal{GM}(\bigotimes_{\substack{i \in I_f^j  }}\boldsymbol{\pi}_i \ ; 
			                         \bigoplus_{\substack{i \in I_f^j  }} \alpha_{i,j} \boldsymbol{\mu}_i \ ; 
			                         \boldsymbol{\sigma}_j^2+\bigoplus_{\substack{i \in I_f^j  }}\alpha_{i,j}^2 \boldsymbol{\sigma}_i^2 )\label{densitygauche}
		\end{eqnarray}
		So when we compare (\ref{densitydroite}) and (\ref{densitygauche}) we see that the number of components in $I_r$ variables differs when subregressions are of length $>1$ (almost 2 predictors) with multiple-class predictors (so the kronecker product is effective). We call this difference in component number "identifiability" in the sense that we try to find the model with the fewest component in $X_f$ (we use the BIC so when comparing two models with the same likelihood, the one with fewer parameters will win). So in this case we have a "better" model (the simplest one) in the group of equivalent-meaning models (permuting variables in some sub-regression).
	So a sufficient condition is $\forall j \in I_r: k_j\geq 2$ with at least two distinct couples $(\boldsymbol{\mu}_j,\boldsymbol{\sigma}_j)$

	If the sufficient condition is not satisfied but we have different variances for $\boldsymbol{X}_f$ and $\boldsymbol{X}_r$,then we don't have identifiability but reverse regressions don't give the same results as the true model, as illustrated in the well-known salary discrimination study \cite{goldberger1984reverse} and explained by others (\cite{leamer1978least},\cite{cameron2005microeconometrics})

	Remark : the uncrossing constraint ($I_2\cap I_1 = \emptyset$) significantly reduces the number of feasible models and thus increases identifiability (because it also reduces the number of models equivalent in interpretation).

	If there are exact sub-regressions, classical methods will fail (singular matrix) and the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not a problem. Moreover, when an exact sub-regression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. CorReg (Our R package) prints a warning to point out exact sub-regressions when found.

%	 As a set of Gaussian mixtures and linear combination of Gaussian mixtures, $\boldsymbol{X}$ follows a multivariate Gaussian mixture model with $K$ components:
%		\begin{eqnarray}
%			f(\boldsymbol{X}|S,\theta)=\sum_{k=1}^Kp_k \Phi(\boldsymbol{X}_r|\boldsymbol{X}_f\boldsymbol{\alpha},S,\theta)\Phi(\boldsymbol{X}_f|S,\theta)
%		\end{eqnarray}	
%
